---
title: "Long-acting buprenorphine"
author: "Your Name"
date: "2025-01-23"
format:
  pptx:
    table-width: 80%
    table-height: 70%
    slide-level: 2
    reference-doc: template.pptx
execute:
  cache: false 
  echo: false
  warning: false
  message: false
---


```{r setup}
#| include: false
library(afcharts)
library(flextable)
library(ggplot2)
library(data.table)
library(lubridate)

main_dt <-
  data.table::fread("data/K3anon_FullDataset_for_VfM.csv")

sir_dt <-
  data.table::fread("data/SIR_table_for_VfM_linked.csv")

invisible(lapply(list.files("R", pattern = "\\.[Rr]$", full.names = TRUE), source))
```
```{r outcomes-calculations-oct}
main_dt <-
  prepare_main_data(main_data = main_dt)

sir_dt <-
  prepare_sir_data(sir_data = sir_dt)


counts_dt <-
  calculate_counts(
    sir_data = sir_dt,
    main_data = main_dt,
    end_date = "2024-10-01"
  )

rates_dt <-
  calculate_rates(counts_data = counts_dt)


mx_rr_t1 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(dt = counts_dt),
    SIMPLIFY = FALSE
  ))

mx_rr_t1[, outcome := "Mortality"][, intervention := "LAB"]

mx_rr_t0 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(dt = counts_dt, invert = TRUE),
    SIMPLIFY = FALSE
  ))

mx_rr_t0[, outcome := "Mortality"][, intervention := "Other OST"]

sc_rr_t1 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(
      dt = counts_dt,
      event = "Successful completion"
    ),
    SIMPLIFY = FALSE
  ))

sc_rr_t1[, outcome := "Successful completion"][, intervention := "LAB"]

sc_rr_t0 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(
      dt = counts_dt,
      invert = TRUE,
      event = "Successful completion"
    ),
    SIMPLIFY = FALSE
  ))

sc_rr_t0[, outcome := "Successful completion"][, intervention := "Other OST"]

relative_risks <- data.table::rbindlist(l = list(mx_rr_t1, mx_rr_t0, sc_rr_t1, sc_rr_t0))

data.table::fwrite(relative_risks, "lab-relative-risks.csv")
```

## Comparative outcomes
### From October to October from 2020 to 2024

## Summary results
```{r result-table-oct}
data.table::setorder(rates_dt, outcome, year)

ft <-
  rates_dt |>
  dplyr::mutate(year = forcats::as_factor(year)) |>
  dplyr::mutate(depot_rate = scales::percent(depot_rate, accuracy = 0.1)) |>
  dplyr::mutate(no_depot_rate = scales::percent(no_depot_rate, accuracy = 0.1)) |>
  flextable() |>
  flextable::set_header_labels(values = c(
    "Year",
    "Outcome",
    "LAB (n)",
    "LAB (%)",
    "No LAB (n)",
    "No LAB (%)"
  )) |>
  flextable::colformat_int(j = 1, big.mark = "") |>
  flextable::fontsize(size = 8) |>
  flextable::padding(
    padding.left = 0.5,
    padding.right = 0.1,
    padding.top = 0.1,
    padding.bottom = 0.1,
    part = "all"
  ) |>
  flextable::height_all(height = 0.2, part = "all") |>
  flextable::align(align = "left", part = "all") |>
  flextable::valign(valign = "center", part = "all") |>
  flextable::autofit()

ft
```
## Mortality rates
```{r mx-rate}
plot_rates(rates_dt, event = "Died")
```
## Relative risk of mortality

- Relative risk of mortality for those receiving long-acting buprenorphine
- Mean relative mortality risk over four years: `{r} round(as.numeric(mx_rr_t1[, mean(rr)]), 2)`
- Plot shows 95% confidence intervals
```{r mx-rr-t1}
plot_rr(mx_rr_t1, n = 3)
```

## Relative risk of mortality

- Relative risk of mortality for those *not* receiving long-acting buprenorphine
- Mean relative mortality risk over four years: `{r} round(as.numeric(mx_rr_t0[, mean(rr)]), 2)`
- Plot shows 95% confidence intervals
```{r mx-rr-t0}
plot_rr(mx_rr_t0, n = 3)
```

## Succesful completion rates

```{r sc-rate}
plot_rates(rates_dt, "Successful completion")
```
## Relative risks: successful completion

- Relative 'risk' of successful completion for those receiving long-acting buprenorphine
- Mean relative risk over four years: `{r} round(as.numeric(sc_rr_t1[, mean(rr)]), 2)`
```{r sc-rr-t1}
plot_rr(sc_rr_t1, n = 3)
```

## Relative risks: successful completion

- Relative 'risk' of successful completion for those *not* receiving long-acting buprenorphine
- Mean relative risk over four years: `{r} round(as.numeric(sc_rr_t0[, mean(rr)]), 2)`
```{r sc-rr-t0}
plot_rr(sc_rr_t0, n = 3)
```

```{r outcomes-calculations-fy}
rm(list = ls())

main_dt <- data.table::fread("data/K3anon_FullDataset_for_VfM.csv")

sir_dt <- data.table::fread("data/SIR_table_for_VfM_linked.csv")

invisible(lapply(list.files("R", pattern = "\\.[Rr]$", full.names = TRUE), source))

main_dt <-
  prepare_main_data(main_data = main_dt)

sir_dt <-
  prepare_sir_data(sir_data = sir_dt)


counts_dt <-
  calculate_counts(
    sir_data = sir_dt,
    main_data = main_dt,
    end_date = "2024-04-01"
  )

rates_dt <-
  calculate_rates(counts_data = counts_dt)


mx_rr_t1 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(dt = counts_dt),
    SIMPLIFY = FALSE
  ))

mx_rr_t1[, outcome := "Mortality"][, intervention := "LAB"]

mx_rr_t0 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(dt = counts_dt, invert = TRUE),
    SIMPLIFY = FALSE
  ))

mx_rr_t0[, outcome := "Mortality"][, intervention := "Other OST"]

sc_rr_t1 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(
      dt = counts_dt,
      event = "Successful completion"
    ),
    SIMPLIFY = FALSE
  ))

sc_rr_t1[, outcome := "Successful completion"][, intervention := "LAB"]

sc_rr_t0 <-
  data.table::rbindlist(mapply(
    FUN = calculate_rr_CIs,
    yr = unique(counts_dt[["year"]]),
    MoreArgs = list(
      dt = counts_dt,
      invert = TRUE,
      event = "Successful completion"
    ),
    SIMPLIFY = FALSE
  ))

sc_rr_t0[, outcome := "Successful completion"][, intervention := "Other OST"]

relative_risks <- data.table::rbindlist(l = list(mx_rr_t1, mx_rr_t0, sc_rr_t1, sc_rr_t0))

data.table::fwrite(relative_risks, "lab-relative-risks-fy.csv")
```
## Comparative outcomes
### Financial year 2020/21 to 2023/24 

## Summary results
```{r result-table-fy}
data.table::setorder(rates_dt, outcome, year)

ft <-
  rates_dt |>
  dplyr::mutate(year = forcats::as_factor(year)) |>
  dplyr::mutate(depot_rate = scales::percent(depot_rate, accuracy = 0.1)) |>
  dplyr::mutate(no_depot_rate = scales::percent(no_depot_rate, accuracy = 0.1)) |>
  flextable() |>
  flextable::set_header_labels(values = c(
    "Year",
    "Outcome",
    "LAB (n)",
    "LAB (%)",
    "No LAB (n)",
    "No LAB (%)"
  )) |>
  flextable::colformat_int(j = 1, big.mark = "") |>
  flextable::fontsize(size = 8) |>
  flextable::padding(
    padding.left = 0.5,
    padding.right = 0.1,
    padding.top = 0.1,
    padding.bottom = 0.1,
    part = "all"
  ) |>
  flextable::height_all(height = 0.2, part = "all") |>
  flextable::align(align = "left", part = "all") |>
  flextable::valign(valign = "center", part = "all") |>
  flextable::autofit()

ft
```
## Mortality rates
```{r mx-rate-fy}
plot_rates(rates_dt, event = "Died")
```
## Relative risk of mortality

- Relative risk of mortality for those receiving long-acting buprenorphine
- Mean relative mortality risk over four years: `{r} round(as.numeric(mx_rr_t1[, mean(rr)]), 2)`
- Plot shows 95% confidence intervals
```{r mx-rr-t1-fy}
plot_rr(mx_rr_t1, n = 2)
```

## Relative risk of mortality

- Relative risk of mortality for those *not* receiving long-acting buprenorphine
- Mean relative mortality risk over four years: `{r} round(as.numeric(mx_rr_t0[, mean(rr)]), 2)`
- Plot shows 95% confidence intervals
```{r mx-rr-t0-fy}
plot_rr(mx_rr_t0, n = 2)
```

## Succesful completion rates

```{r sc-rate-fy}
plot_rates(rates_dt, "Successful completion")
```
## Relative risks: successful completion

- Relative 'risk' of successful completion for those receiving long-acting buprenorphine
- Mean relative risk over four years: `{r} round(as.numeric(sc_rr_t1[, mean(rr)]), 2)`
```{r sc-rr-t1-fy}
plot_rr(sc_rr_t1, n = 2)
```

## Relative risks: successful completion

- Relative 'risk' of successful completion for those *not* receiving long-acting buprenorphine
- Mean relative risk over four years: `{r} round(as.numeric(sc_rr_t0[, mean(rr)]), 2)`
```{r sc-rr-t0-fy}
plot_rr(sc_rr_t0, n = 2)
```
